ERSPAN Support for Linux

### 2018-10-09 paper.tex
add example

\usepackage{graphicx}
\usepackage{url}
\usepackage{listings}
\usepackage{amsmath}
\usepackage[font={small}]{caption}

\newcommand{\dfn}[1]{\textit{#1}} % For initial definitions of terms

@@

\section{Use Cases}
ERSPAN for IPv4 was implemented under net/ipv4/ip\_gre.c and was
upstreamed to Linux kernel in 4.14~\cite{erspanipv4}.
The ERSPAN for IPv6

\subsection{IPv4}

gre: introduce native tunnel support for ERSPAN

The ERSPAN implementation for IPV
\subsection{IPv6}
\subsection{Limitation}
DF bit is set to prevent fragmentation
• GRE Header protocol type of 0x88BE
• PFC3 and above supports ERSPAN (sup720, sup32)
• Cisco ASR supports ERSPAN as well
• ERSPAN ID uniquely identifies source sessions

%https://sharkfestus.wireshark.org/sharkfest.10/D-2_Chung%20A%20Variety%20of%20Ways%20to%20Capture%20and%20Analyze%20Packets.pdf

\subsection{fragmentation}
\section{Use Cases}
Port mirroring and monitoring overview
Port mirroring is a method of monitoring network traffic that forwards a copy of each incoming or outgoing packet from one port on a network switch to another port where the packet can be analyzed. Port mirroring can be used as a diagnostic tool or debugging feature, especially for preventing attacks. Port mirroring can be managed locally or remotely.
You can configure port mirroring, by assigning a port (known as the Monitor port), from which the packets are copied and sent to a destination port (known as the Mirror port). All packets received on the Monitor port or issued from it, are forwarded to the second port. You next attach a protocol analyzer on the mirror port to monitor each segment separately. The analyzer captures and evaluates the data without affecting the client on the original port.

\subsection{Linux iproute2}\label{iproute2}
\subsection{eBPF}\label{ebpf}
\subsection{Open vSwitch}\label{ovs}
\subsection{Cisco Switch}
    gre: introduce native tunnel support for ERSPAN

\begin{verbatim}
    monitor session 100 type erspan-source
      erspan-id 123
      vrf default
      destination ip 172.16.1.200
      source interface Ethernet1/11 both
      source interface Ethernet1/12 both
      no shut
    monitor erspan origin ip-address 172.16.1.100 global
\end{verbatim}

\section{Conclusion}
\section{Acknowledgments}
\section{Future Work}

>>>>

\usepackage{graphicx}
\usepackage{url}
\usepackage{listings}
\usepackage{amsmath}
\usepackage[font={small}]{caption}
\newcommand{\mycomment}[1]{}
\newcommand{\dfn}[1]{\textit{#1}} % For initial definitions of terms

@@

\section{Example Use Case}
\begin{figure}
{\scriptsize
\begin{verbatim}
 session 10            Linux, session 20        Linux, session 30
+----------+         +-------------------+      +----------------+
| Physical |         |     VM1  VM2 ...  |      |     linux      |
| Machines |         | 10.1.1.3  |       |      |    netdevs     |
+----------+         |  +--------------+ |      |      |         |
    | links          |  | Open vSwitch | |      | ERSPAN 10.1.1.4|
    | 10.1.1.2       |  +--------------+ |      | netdev         |
+------------+       +-------||----------+      +-||------------+ 
|Cisco switch|               ||                   ||
+------------+               || ERSPAN            || ERSPAN
   || ERSPAN tunnel          || tunnel            || tunnel
   || (192.168.1.2)          || (192.168.1.3)     || (192.168.1.4)
    /~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\     +-------+ 
    {       Layer 3 IPv4, Ipv6 network             } === |Traffic|
    \~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~/     |Sniffer|
                192.168.1.*                              +-------+
                                                        192.168.1.1
\end{verbatim}   
}
\vspace{-0.5em}
\caption{Example of creating three ERSPAN monitoring sessions, $10, 20, 30$,
in a $10.1.1.*$ internal network, mirroring traffic over a $192.168.1.*$ IP network.}
\label{example}
\vspace{-1.0em}
\end{figure}

We use Figure~\ref{example} as an example topology to demostrate
the three configuration ways of ERSPAN.
Assuming a network administrator wants to monitor a network consists
of 1) physical machines connected to Cisco switches, 2)
virtualized Linux machine with multiple VMs deployed and virtual switch
(openvswitch.ko) enforcing the fowarding policies, and
3) non-virtualized Linux physical machines, e.g., service nodes
in data center such as gateways.
Assuming all the monitored servers are under IP subnet of $10.1.1.*$,
and We place a traffic sniifer over another IP network of $192.168.1.*$.
The following subsection describes the configuration for each case.

\subsection{Cisco Switch}
We use Nexus 5000 switch and configure its ERSPAN tunnel
on ports 11 and 12 as below.
\begin{verbatim}
    monitor session 10 type erspan-source
      erspan-id 10
      vrf default
      destination ip 192.168.1.1
      source interface Ethernet1/11 both
      source interface Ethernet1/12 both
      no shut
    monitor erspan origin ip-address 192.168.1.2 global
\end{verbatim}

\subsection{openvswitch.ko}\label{ovs}
Open vSwitch consists of a userspace daemon, ovs-vswitchd, and a kernel
datapath implementation, openvswitch.ko.
This example shows a case where we only use the netlink API and openvswitch.ko
module, without the ovs-vswitchd daemon.
ovs-dpctl is a stand-alone tool which programs openvswitch.ko
through network api, see Joes' paper
\begin{verbatim}
ip link add dev myerspan type erspan external
ovs-dpctl add-dp mydp
ovs-dpctl add-if mydp myerspan
ovs-dpctl add-if mydp veth1 // connected to VM1
ovs-dpctl add-flow \
    "in_port(2)" \  // any packets matching in_port=2
    "set(tunnel(tun_id=20,dst=192.168.1.1,ttl=64,\
    erspan(ver=2,dir=1,hwid=0x4),flags(df|key))),3"
\end{verbatim}

\subsection{eBPF and iproute2}\label{iproute2}

Assuming we want to make a copy of all traffic from the physical
device eth1, and encapsulate them through ERSPAN tunnel.
We first create a native-mode ERSPAN tunnel using ip-link command,
and make a copy of all traffic from eth1 to the ERSPAN tunnel netdev.
%see net/ip6_gre_headroom.sh
\begin{verbatim}
ip link add dev myerspan type erspan seq key 30 \
    local 192.168.1.4 remote 192.168.1.1 \
    erspan_ver 1 erspan 123
tc filter add dev eth1 ingress pref 1000 matchall skip_hw \
    action mirred egress mirror dev myerspan
\end{verbatim}

For the eBPF tunnel cases,
we create a metadata mode erspan tunnel, and set the
remote ip and tunnel id to 30, attach the eBPF program,
and create the fowarding rule using tc.
\begin{verbatim}
ip link add dev myerspan type erspan external
tc qdisc add dev myerspan clsact
tc filter add dev myerspan bpf da obj test_tunnel_kern.o section set_erspan
tc filter add dev eth1 ingress pref 1000 matchall skip_hw \
    action mirred egress mirror dev myerspan
\end{verbatim}

\section{Conclusion}
\section{Future Work}
\section{Acknowledgments}
